BIP Architectures and Open pNets

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
nouvelel figure OA detaille en page 39
Open automaton

\noteLH{a pred is a g a post is a u (modified macros!)}
\renewcommand{\Pred}{g}
\renewcommand{\Post}{u}
The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes the actions of several holes, 
the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{defn:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes  and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {{\alpha}}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
        is an action of the hole $j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
	\assigns{\variables}$\ is 
	a set of assignments that are the effects of the transition.
Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}
%\begin{definition}[Open transitions]
%	\label{def:OpenTransitions}
%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
%we omit indices on $\goesto{}$ and that they are always clear from the 
%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
%	I}$} of LTSs, a
%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
%	a structure of the form:	
%	\begin{mathpar}
%	\inferrule*[myfraction=\reddottedrule]
%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
%	{s \OTarrow {v}s'}
%	\end{mathpar}
%	Where $s, s'\in\mathcal{S}$ and for all
%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
%        is a transition of the hole $j$}, for any action $b_j$ in the
%        sort $\Sort_j$.  
%        of this open transition. \Pred\ is a predicate 
%	over the different variables of the
%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
%	hold \emph{after the open transition}, they are represented as a substitution of the 
%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
%	would like to just put $\Post_=e$}
%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
%	variables of the open transition.
%\end{definition}

@@

\end{example}

@@

The second one, $OT_3$, correspond to the firing of the connector
$''tick, fail, fail''$, with the hole B performing action $fail$......

It is important to understand the difference between the red dotted rule and a normal 
inference rule. They correspond to two different logical levels.
 The open transition is itself a logical implication, but using a simple logic (with the 
 expressive power that is given to the predicate and necessary include logical 
 propositions and equality). We differentiate classical (black) inference rules that use 
 an expressive logic and are paper rules from open transition rules that use a simpler 
 logic, 
 will be embedded into automata transitions, and could typically be handled in a 
 mechanical way.

@@

OTs simplifiees a la main:

>>>>

\noteLH{a pred is a g a post is a u (modified macros!)}
\renewcommand{\Pred}{g}
\renewcommand{\Post}{u}
The semantics of an open pNets is expressed as an open automaton, i.e., an automaton where each transition composes the actions of several holes, 
the transition occurs if some predicates hold, and can involve a 
 state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{defn:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes  and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {{\alpha}}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
        is an action of the hole $j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
	\assigns{\variables}$\ is 
	a set of assignments that are the effects of the transition.
Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}
%\begin{definition}[Open transitions]
%	\label{def:OpenTransitions}
%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
%we omit indices on $\goesto{}$ and that they are always clear from the 
%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
%	I}$} of LTSs, a
%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
%	a structure of the form:	
%	\begin{mathpar}
%	\inferrule*[myfraction=\reddottedrule]
%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
%	{s \OTarrow {v}s'}
%	\end{mathpar}
%	Where $s, s'\in\mathcal{S}$ and for all
%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
%        is a transition of the hole $j$}, for any action $b_j$ in the
%        sort $\Sort_j$.  
%        of this open transition. \Pred\ is a predicate 
%	over the different variables of the
%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
%	hold \emph{after the open transition}, they are represented as a substitution of the 
%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
%	would like to just put $\Post_=e$}
%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
%	variables of the open transition.
%\end{definition}

@@

@@

The second one, $OT_3$, correspond to the firing of the connector
$''tick, fail, fail''$, with the hole B performing action $fail$......
\end{example}

It is important to understand that the red dotted rule expresses an implication but at a different logical level compared to  a normal 
inference rule. 
 The open transition is  a logical implication that uses a simple logic with the 
 expressive power  given by the predicate algebra (it must include logical 
 propositions and equality). We differentiate classical (black) inference rules that use 
 an expressive (higher order) logic and are paper rules from open transition rules that use a simpler  logic,  define automata transitions, and could  be handled 
 mechanically.

@@

OTs simplifiees a la main:
\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{TimerOADetailed}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}
